Interpretable Machine Learning for Science \\ with PySR and SymbolicRegression.jl

### 2023-05-02 src/tex/ms.tex
Link GitHubs from abstract

\newcommand\we{we\xspace}
\newcommand\We{We\xspace}
\newcommand\Our{Our\xspace}
\newcommand\our{our\xspace}
\newcommand\pysr{\textsc{PySR}\xspace}
\newcommand\pysrjl{\textsc{SymbolicRegression.jl}\xspace}
\newcommand\eureqa{\textsc{Eureqa}\xspace}
\newcommand\sr{SR\xspace}
\newcommand\Sr{SR\xspace}
\newcommand{\todo}[1]{{\color{red} #1}}

\usepackage{cleveref} \begin{document}
\thispagestyle{empty}
\newcommand\myhref[2]{\textsf{\textcolor{blue}{\href{#1}{#2}}}}
\newcommand\giturl{\myhref{https://github.com/MilesCranmer/pysr_paper}{github.com/MilesCranmer/pysr\_paper}}

@@

\twocolumn[\begin{@twocolumnfalse}
\maketitle
\begin{abstract}
\pysr is an open-source library for practical \textit{symbolic regression}, a type of machine learning which aims to discover human-interpretable symbolic models.
\pysr was developed to democratize and popularize symbolic regression for the sciences, and is built on a high-performance distributed backend, a flexible search algorithm, and interfaces with several deep learning packages.
\pysr's internal search algorithm is a multi-population evolutionary algorithm, which consists of a unique evolve-simplify-optimize loop, designed for optimization of unknown scalar constants in newly-discovered empirical expressions.
\pysr's backend is an extremely optimized Julia library \pysrjl, which can be used directly from Julia. It is capable of fusing user-defined operators into SIMD kernels at runtime, performing automatic differentiation, and distributing populations of expressions to thousands of cores across a cluster.
In describing this software, we also introduce a new benchmark, ``\textit{EmpiricalBench},’’ to quantify the applicability of symbolic regression algorithms in science.
This benchmark measures recovery of historical empirical equations from original and synthetic datasets.
\end{abstract}
\end{@twocolumnfalse}
]

>>>>

\newcommand\we{we\xspace}
\newcommand\We{We\xspace}
\newcommand\Our{Our\xspace}
\newcommand\our{our\xspace}
\newcommand\pysr{\textsc{PySR}\xspace}
\newcommand\pysrjlabs{\mbox{\textsc{SymbolicRegression.jl}}\xspace}
\newcommand\pysrjl{\textsc{SymbolicRegression.jl}\xspace}
\newcommand\eureqa{\textsc{Eureqa}\xspace}
\newcommand\sr{SR\xspace}
\newcommand\Sr{SR\xspace}
\newcommand{\todo}[1]{{\color{red} #1}}

\usepackage{cleveref} \begin{document}
\newcommand\myhref[2]{\textsf{\textcolor{blue}{\href{#1}{#2}}}}
\newcommand\giturl{\myhref{https://github.com/MilesCranmer/pysr_paper}{github.com/MilesCranmer/pysr\_paper}}

@@

\twocolumn[\begin{@twocolumnfalse}
\maketitle
\begin{abstract}
\addtocounter{footnote}{2}
\pysr\footnotemark{} is an open-source library for practical \textit{symbolic regression}, a type of machine learning which aims to discover human-interpretable symbolic models.
\pysr was developed to democratize and popularize symbolic regression for the sciences, and is built on a high-performance distributed backend, a flexible search algorithm, and interfaces with several deep learning packages.
\pysr's internal search algorithm is a multi-population evolutionary algorithm, which consists of a unique evolve-simplify-optimize loop, designed for optimization of unknown scalar constants in newly-discovered empirical expressions.
\pysr's backend is an extremely optimized Julia library \pysrjlabs\footnotemark{},
which can be used directly from Julia. It is capable of fusing user-defined operators into SIMD kernels at runtime, performing automatic differentiation, and distributing populations of expressions to thousands of cores across a cluster.
In describing this software, we also introduce a new benchmark, ``\textit{EmpiricalBench},’’ to quantify the applicability of symbolic regression algorithms in science.
This benchmark measures recovery of historical empirical equations from original and synthetic datasets.
\end{abstract}
\end{@twocolumnfalse}
]

\addtocounter{footnote}{-1}
\footnotetext{\textsf{github.com/MilesCranmer/PySR}}
\addtocounter{footnote}{1}
\footnotetext{\textsf{github.com/MilesCranmer/SymbolicRegression.jl}}
